Vertical and oblique transmission with fluctuating transmission

### 2018-03-20 ms/fluctuating_oblique.tex
UL addition to constant selection

First, fixations of $A$ and $B$ ($x^*=0$ and $x^*=1$, respectively) are both equilibria, as they solve $x''=x$.
Second, because $x'/x = 1+\frac{\rho_1 s (1-x)}{1+sx} > 1$ and $x''/x = 1+\frac{\rho_2 s (1-x)}{1+sx} > 1$, the frequency of $A$ increases every generation and $x^*=1$ is globally stable.
Therefore, we find that fluctuations in the mode of transmission ($\rho$) without fluctuations in selection lead to fixation of the favored phenotype without any stable polymorphisms.

>>>>

First, fixations of $A$ and $B$ ($x^*=0$ and $x^*=1$, respectively) are both equilibria, as they solve $x''=x$.
Second, when $s>0$ ($s<0$) because $x'/x = 1+\frac{\rho_1 s (1-x)}{1+sx} > 1$ ($<1$) and $x''/x = 1+\frac{\rho_2 s (1-x)}{1+sx} > 1$ ($<1$), the frequency of $A$ ($B$) increases every generation and $x^*=1$ ($x^*=0$) is globally stable.
Therefore, we find that fluctuations in the mode of transmission ($\rho$) without fluctuations in selection lead to fixation of the favored phenotype without any stable polymorphisms.
